%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = pdflatex
% vim: spell spelllang=en_gb


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This extended-abstract version of this paper was submitted, accepted and presented to/at the CLARIN conference 2024. 
% The post-proceedings paper is a work in progress and still pending submission and further peer review.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\documentclass[a4paper,11pt]{article}
\usepackage{CLARIN2024}
% - - - - - - - IMPORTANT - - - - - - - -
% The next three lines allow XeLaTeX, graphics import and hyperlinks, set font and language
%\usepackage{xltxtra,polyglossia,graphicx,hyperref}
%\setmainfont[Mapping=tex-text]{Times}
%\setdefaultlanguage{english}
% If for some reason the above three lines are not compatible with your LaTeX installation,
% comment out the above three instructions and uncomment the following four instead:
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[
    backend=biber,
    style=apa,
    natbib=true,
    ]{biblatex}
\addbibresource{tooldiscovery.bib} % add your own bibliography into the format provided in this file


% JSON highlighting, copied from https://tex.stackexchange.com/questions/83085/how-to-improve-listings-display-of-json-files
\definecolor{eclipseStrings}{RGB}{42,0.0,255}
\definecolor{eclipseKeywords}{RGB}{127,0,85}
\colorlet{numb}{magenta!60!black}
\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily\footnotesize,
    commentstyle=\color{eclipseStrings}, % style of comment
    stringstyle=\color{eclipseKeywords}, % style of strings
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    string=[s]{"}{"},
    comment=[l]{:\ "},
    morecomment=[l]{:"},
    literate=
        *{0}{{{\color{numb}0}}}{1}
         {1}{{{\color{numb}1}}}{1}
         {2}{{{\color{numb}2}}}{1}
         {3}{{{\color{numb}3}}}{1}
         {4}{{{\color{numb}4}}}{1}
         {5}{{{\color{numb}5}}}{1}
         {6}{{{\color{numb}6}}}{1}
         {7}{{{\color{numb}7}}}{1}
         {8}{{{\color{numb}8}}}{1}
         {9}{{{\color{numb}9}}}{1}
}


%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

%\usepackage{covington} % if needed, for linguistic examples

\title{From source code to the SSH Open Marketplace -- a software metadata journey}

% - - - - - - - IMPORTANT - - - - - - -
% Leave the author information empty until your paper has been accepted 

% Uncomment the following line ONLY if you need two author rows
%\setlength\titlebox{80mm} 

\author{Maarten van Gompel \\
  KNAW Humanities Cluster \\
  Amsterdam, the Netherlands \\
  {\tt proycon@anaproy.nl} %\And % if needed: this makes a second column
%  Department (optional)\\
%  University Name without city \\
%  City, Country \\
% {\tt email@domain} \\
% \AND % if needed: this makes a second row
%  Third Author \\
%  Department (optional)\\
%  University of City, Country \\
%  {\tt email@domain} \\\And
%  Fourth Author \\
%  Department (optional)\\
%  University Name without city \\
%  City, Country \\
%  {\tt email@domain} \\
} 

\date{}

\begin{document}
\maketitle
\begin{abstract}
We developed a harvesting pipeline that automatically and periodically harvests
software metadata from the source \citep{CLARINCONF2024}. Software source code is often accompanied,
by metadata in various metadata formats, living together in the same source
code repository. We automatically convert all metadata we can find there to a
single CodeMeta representation. This is a linked open data vocabulary that
re-uses and extends schema.org. It acts as a pivot language for software
metadata. 

The harvesting pipeline was built for the Dutch CLARIAH project to catalogue all
the tools delivered in that project. In the current follow-up study, we seek
integration with existing software catalogues and worked on extending the
pipeline to ingest its data into the SSH Open Marketplace \citep{MPSPEC,MPINTEROP,MPDATAPOP}. We do so by
translating the Codemeta to Marketplace API calls. We will discuss the
solutions and challenges we encountered on this path. 
\end{abstract}


\section*{Acknowledgements}

The FAIR Tool Discovery track has been developed as part of the CLARIAH-PLUS
project (NWO grant 184.034.023), as part of the Shared Development Roadmap.

Connectivity to the SSHOC Open Marketplace is developed in the 
SSHOC-NL project as part of Task 1.1.

\printbibliography

\end{document}
